---
output: html_document
---

## Stock Status Relative to Management Targets

The stock status factor incorporates scoring based upon the estimated stock status (Table 5) or Productivity Susceptibility Analysis (PSA) values for unassessed species (Table 6). Species that either have been estimated to be below the management target or high PSA scores receive higher scores with species estimated to be below the Minimum Stock Size Threshold (MSST) and are estimated to have declining spawning output in recent years receiving the highest scores. Species that are estimated to be well above the management target or are unassessed and have low PSA values receive the lowest scores. Where available, the percentage of unfished output estimated in the terminal year of the most recent assessment for each species is used as the basis for scoring. The stock status for species with multiple assessment areas have calculated coastwide stock status based on the coastwide summed spawning output in the final year of the most recent assessment. 
 

```{r, results = 'asis', echo = FALSE}
suppressWarnings(library(gt))

abund = data.frame(matrix(NA, 10, 2))
colnames(abund) <- c("Score", "Stock Status")

abund[1,]  = c(1, "Abundance is greater than 2 times the target" )
abund[2,]  = c(2, "Abundance is between 1.5 and 2 times the target")
abund[3,]  = c(3, "Abundance is between 1.1 and 1.5 times the target or abundance is unknown and the vulnerability is low (PSA < 1.8)")
abund[4,]  = c(4, "Abundance is between 0.9 and 1.1 times the target")
abund[5,]  = c(5, "Abundance is between MSST and 0.9 times that target and is increasing in recent years or abundance is unknown and the vulnerability is moderate (1.8 =< PSA < 2.0)")
abund[6,]  = c(6, "Abundance is between MSST and 0.9 times that target and is stable in recent years")
abund[7,]  = c(7, "Abundance is between MSST and 0.9 times that target and is declining in recent years or abundance is unknown and the vulnerability is high (PSA >= 2).")
abund[8,]  = c(8, "Abundance is below the MSST and increasing in recent years")
abund[9,]  = c(9, "Abundance is below the MSST and stable in recent years")
abund[10,] = c(10, "Abundance is below the MSST and decreasing in recent years")

abund_tbl <- abund |>
  gt::gt() |>
  tab_header(
    title = "Table 5: Factor sores applied based the estimated fraction of unfished spawning output (i.e., abundance) relative to the species-specific management targets from the most recent assessment or the PSA score for un-assessed species."
  ) |>
  gt::tab_options(
    table.font.size = 12
  ) |>
  gt::cols_align(
    align = "left",
    columns = everything()
  )

abund_tbl

```



```{r, results = 'asis', echo = FALSE}
library(gt)

psa <- read.csv("tables/psa.csv", header = TRUE) 
psa <- psa[-c(2)]
colnames(psa) <- c("Species", "PSA Score")

psa_tbl <- psa |>
  gt() |>
  tab_header(
    title = "Table 6: The Productivity Susceptibility Analysis (PSA) scores by species. Higher PSA values indicate higher vulnerability."
  ) |>
  cols_align(
    align = "left",
    columns = "Species"
  ) |>
  cols_align(
    align = "right",
    columns = "PSA Score"
  ) |>
  data_color(
    columns = "PSA Score", method = "numeric", palette = "viridis"
  )

psa_tbl
  
```